### 2023-11-09 manuscript/manuscript.Rmd
Update the assignment parameters in the methods section

negative_mode_adducts <-  brachy_FIE_HRMS_parameters_molecular_formula_assignment %>% 
  assignments::adducts() %>% 
  .$n %>% 
  stringr::str_replace_all(']1-',']^1-^') %>% 
  stringr::str_replace_all(']2-',']^2-^') %>% 
  stringr::str_replace_all('Cl37','^37^Cl') %>% 
  str_as_written_list()
positive_mode_adducts <-   brachy_FIE_HRMS_parameters_molecular_formula_assignment %>% 
  assignments::adducts() %>% 
  .$p %>% 
  stringr::str_replace_all(stringr::coll(']1+'),']^1+^') %>% 
  stringr::str_replace_all(stringr::coll(']2+'),']^2+^') %>% 
  stringr::str_replace_all('K41','^41^K') %>% 
  str_as_written_list()
```

@@

The negative ionisation mode adducts included: `r negative_mode_adducts`.
The positive ionisation mode adducts included: `r positive_mode_adducts`.
All adduct mass, charge and molecule information can be found in Additional file 3 (Table S2).
The isotopes included single and double ^13^C and ^18^O for the *B.distachyon* matrices and additionally ^34^S for the spiked urine.
The isotopic mass information used can be found in Additional file 3 (Table S3).
For all matrices, `r nrow(mzAnnotation::transformation_rules)` transformations were based on the transitions of common metabolic reactions found in primary metabolism.
These transformations can be found in Additional file 3 (Table S4).

@@

Generated molecular formulas were restricted to only include the elements C, H, N, O, P and S.
For a given $M$, the maximum allowed element frequencies for generated molecular formulas were restricted using the following terms: $C = M/12$, $H = 2C$, $N,O = C/2$, $P,S = C/4$.
The calculated frequencies were rounded to the nearest integer value.
Molecular formula generation was conducted for each $M$ value within a mass deviation range of $\pm$ 6 ppm.
This generation was exhaustive, using the brute force approach of the HR2 generator, without the application of the golden rules proposed by @kind2007.

@@

To calculate $AIS$, the possible adducts within each ionisation mode were ranked from most probable to least probable and assigned a score ($a$) with the most probable being $n-1$, $n$ being the number of adducts within that ionisation mode and least probable adduct a score of 0. 
The adduct rank scores used for the assignment were based on the adduct order specified in Section \@ref(relationships) for all matrices.

Similarly, for the possible isotopes, these were also ranked from most (non-isotopic) to least probable and assigned a score ($i$) as for the adducts.
The isotopic rank scores used for the assignment of the *B.distachyon* matrices were as follows: Non-isotopic = 3, ^13^C = 2, ^18^O = 1, ^13^C2 = 0.
For the spiked urine matrices, the isotopic rank scores were: Non-isotopic = 4, ^13^C = 3, ^18^O = 2, ^34^S = 1, ^13^C2 = 0.

>>>>

negative_mode_adducts <-  brachy_FIE_HRMS_parameters_molecular_formula_assignment %>% 
  assignments::adducts() %>% 
  .$n %>% 
  stringr::str_replace_all(']1-',']^1-^') %>% 
  stringr::str_replace_all(']2-',']^2-^') %>% 
  stringr::str_replace_all('Cl37','^37^Cl') %>% 
  str_as_written_list()

positive_mode_adducts <-   brachy_FIE_HRMS_parameters_molecular_formula_assignment %>% 
  assignments::adducts() %>% 
  .$p %>% 
  stringr::str_replace_all(stringr::coll(']1+'),']^1+^') %>% 
  stringr::str_replace_all(stringr::coll(']2+'),']^2+^') %>% 
  stringr::str_replace_all('K41','^41^K') %>% 
  str_as_written_list()

standards_pos_adducts <-   standards_parameters_molecular_formula_assignment %>% 
  assignments::adducts() %>% 
  .$p %>% 
  stringr::str_replace_all(stringr::coll(']1+'),']^1+^') %>% 
  stringr::str_replace_all(stringr::coll(']2+'),']^2+^') %>% 
  stringr::str_replace_all('K41','^41^K') %>% 
  str_as_written_list()
```

@@

The negative ionisation mode adducts included: `r negative_mode_adducts`.
The positive ionisation mode adducts included: `r positive_mode_adducts`.
All adduct mass, charge and molecule information can be found in Additional file 3 (Table S2).
The isotopes included ^13^C and ^18^O for the *B.distachyon* matrices and additionally ^34^S for the standards mix and spiked urine.
The isotopic mass information used can be found in Additional file 3 (Table S3).
For all matrices, `r nrow(mzAnnotation::transformation_rules)` transformations were based on the transitions of common metabolic reactions found in primary metabolism.
These transformations can be found in Additional file 3 (Table S4).

@@

Generated molecular formulas were restricted to only include the elements C, H, N, O, P and S.
For a given $M$, the maximum allowed element frequencies for generated molecular formulas were restricted using the following terms: $C = M/12$, $H = 2C$, $N,O = C/2$, $P,S = C/4$.
The calculated frequencies were rounded to the nearest integer value.
Molecular formula generation was conducted for each $M$ value within a mass deviation range of $\pm$ `r search_ppm` ppm.
This generation was exhaustive, using the brute force approach of the HR2 generator, without the application of the golden rules proposed by @kind2007.

@@

To calculate $AIS$, the possible adducts within each ionisation mode were ranked from most probable to least probable and assigned a score ($a$) with the most probable being $n-1$, $n$ being the number of adducts within that ionisation mode and least probable adduct a score of 0. 
The adduct rank scores used for the assignment were based on the adduct order specified in Section \@ref(relationships) for the *B. distachyon* matrices. For the standards mix and spiked urine, an alternative order of `r standards_pos_adducts` was used for the positive mode adducts.

Similarly, for the possible isotopes, these were also ranked from most (non-isotopic) to least probable and assigned a score ($i$) as for the adducts.
The isotopic rank scores used for the assignment of the *B.distachyon* matrices were as follows: Non-isotopic = 2, ^13^C = 1, ^18^O = 0.
For the standards mix and spiked urine matrices, the isotopic rank scores were: Non-isotopic = 3, ^13^C = 2, ^18^O = 1, ^34^S = 0.
